Modern BTree\\ techniques

### 2020-01-03 btree/presentation.tex
Btree basic

@@

    \begin{itemize}[label={\MVRightarrow}]
        \item <+-> Graefe, Goetz and Harumi A. Kuno. “Modern B-tree
            techniques.” IEEE 27th International Conference on Data
            Engineering, 2011.
        \item <+-> D. Comet, "Ubiquitous B-tree", ACM Comp. Surv., vol. 11, no.
            2, 1979.
    \end{itemize}
\end{frame}

@@

            \draw[->, btree-line] (pointer11.south) -- (pointer12.north);
            \draw[->, btree-line] (pointer21.south)
                .. controls ([yshift=-1cm] pointer21) and ([yshift=1cm] pointer14) ..
                (pointer14.north);
            \draw[->, btree-line] (pointer31.south)
                .. controls ([yshift=-1cm] pointer31) and ([yshift=1cm] pointer13) ..
                (pointer13.north);
        \end{tikzpicture}

@@

@@

>>>>

\newcommand{\btreenodenotfull}[5] {
    \path
        \newcounter{themenumber}
        \newcounter{classnumber}
        \newcounter{imagenumber}
        \forloop{themenumber}{1}{\value{themenumber} < 24}{
            % \hline <-- Error here
            \arabic{themenumber}
            \forloop{classnumber}{0}{\value{classnumber} < 2}{
                \forloop{imagenumber}{1}{\value{imagenumber} < 6}{
                    & \includegraphics[scale=2]{
                        ../../results/\arabic{themenumber}/\arabic{classnumber}_\arabic{imagenumber}.eps
                    }
                }
            }
        }
      node[btree-pointer, #2, #3] (pointer1#1) {}
      node[btree-key, right=0 of pointer1#1, #3] (sep1#1) {}
      node[btree-key, left=0 of pointer1#1, #3] (sep2#1) {}
      node[btree-pointer, right=0 of sep1#1, #3] (pointer2#1) {}
      node[btree-pointer, left=0 of sep2#1, #3] (pointer3#1) {}
      node[btree-key, right=0 of pointer2#1, #3] (sep3#1) {}
      node[btree-key, left=0 of pointer3#1, #3] (sep4#1) {}
      node[draw, inner sep=0, behind path, #4,
          fit=(pointer1#1)(pointer2#1)(pointer3#1)
              (sep1#1)(sep2#1)(sep3#1)(sep4#1)
      ] (node#1) {};

@@

    \begin{itemize}[label={\MVRightarrow}]
        \item <+-> D. Comet, "Ubiquitous B-tree", ACM Comp. Surv., vol. 11, no.
            2, 1979.
        \item <+-> Graefe, Goetz and Harumi A. Kuno. “Modern B-tree
            techniques.” IEEE 27th International Conference on Data
            Engineering, 2011.
    \end{itemize}
\end{frame}

@@

            \draw[->, btree-line] (pointer11.south) -- (pointer12.north);
            \draw[->, btree-line] (pointer21.south)
                .. controls ([yshift=-1cm] pointer21) and ([yshift=1cm] pointer14) ..
                (pointer14.north);
            \draw[->, btree-line] (pointer31.south)
                .. controls ([yshift=-1cm] pointer31) and ([yshift=1cm] pointer13) ..
                (pointer13.north);

            \coordinate[right=0.5cm of sep34.east] (link-sep34);
            \draw[btree-hide] ([yshift=0.1cm]sep34.east) -- ([yshift=0.1cm]link-sep34.west);
            \coordinate[left=0.5cm of sep43.west] (link-sep43);
            \draw[btree-hide] ([yshift=0.1cm]sep43.west) -- ([yshift=0.1cm]link-sep43.east);
        \end{tikzpicture}

@@

            \draw[->, btree-line] (pointer11.south) -- (pointer12.north);
            \draw[->, btree-line] (pointer21.south)
                .. controls ([yshift=-1cm] pointer21) and ([yshift=1cm] pointer14) ..
                (pointer14.north);
            \draw[->, btree-line] (pointer31.south)
                .. controls ([yshift=-1cm] pointer31) and ([yshift=1cm] pointer13) ..
                (pointer13.north);

            \draw[->, btree-line] ([yshift=0.1cm]sep33.east) -- ([yshift=0.1cm]sep42.west);
            \draw[->, btree-line] ([yshift=0.1cm]sep32.east) -- ([yshift=0.1cm]sep44.west);
            \coordinate[right=0.5cm of sep34.east] (link-sep34);
            \draw[->, btree-line] ([yshift=0.1cm]sep34.east) -- ([yshift=0.1cm]link-sep34.west);
            \coordinate[left=0.5cm of sep43.west] (link-sep43);
            \draw[btree-hide] ([yshift=0.1cm]sep43.west) -- ([yshift=0.1cm]link-sep43.east);
        \end{tikzpicture}

        \onslide<5>
        \begin{tikzpicture}[]
            \btreenode{1}{}{}{btree-branch}{}
            \btreenode{2}{below=1cm of node1.south}
                {}{btree-leaf}{show-pointers}
            \btreenode{3}{below=1cm of node1.south west, xshift=-3cm}
                {}{btree-leaf}{show-pointers}
            \btreenode{4}{below=1cm of node1.south east, xshift=3cm}
                {}{btree-leaf}{show-pointers}

            \draw[->, btree-line] (pointer11.south) -- (pointer12.north);
            \draw[->, btree-line] (pointer21.south)
                .. controls ([yshift=-1cm] pointer21) and ([yshift=1cm] pointer14) ..
                (pointer14.north);
            \draw[->, btree-line] (pointer31.south)
                .. controls ([yshift=-1cm] pointer31) and ([yshift=1cm] pointer13) ..
                (pointer13.north);

            \draw[->, btree-line] ([yshift=0.1cm]sep33.east) -- ([yshift=0.1cm]sep42.west);
            \draw[->, btree-line] ([yshift=0.1cm]sep32.east) -- ([yshift=0.1cm]sep44.west);
            \draw[<-, btree-line] ([yshift=-0.1cm]sep33.east) -- ([yshift=-0.1cm]sep42.west);
            \draw[<-, btree-line] ([yshift=-0.1cm]sep32.east) -- ([yshift=-0.1cm]sep44.west);
            \coordinate[right=0.5cm of sep34.east] (link-sep34);
            \draw[->, btree-line] ([yshift=0.1cm]sep34.east) -- ([yshift=0.1cm]link-sep34.west);
            \coordinate[left=0.5cm of sep43.west] (link-sep43);
            \draw[->, btree-line] ([yshift=0.1cm]sep43.west) -- ([yshift=0.1cm]link-sep43.east);
        \end{tikzpicture}

        \onslide<6>
        \begin{tikzpicture}[]
            \btreenode{1}{}{}{btree-branch}{}
            \btreenode{2}{below=1cm of node1.south}
                {}{btree-leaf}{show-pointers}
            \btreenode{3}{below=1cm of node1.south west, xshift=-3cm}
                {}{btree-leaf}{show-pointers}
            \btreenode{4}{below=1cm of node1.south east, xshift=3cm}
                {}{btree-leaf}{show-pointers}

@@

            \draw[->, btree-line] ([yshift=0.1cm]sep33.east) -- ([yshift=0.1cm]sep42.west);
            \draw[->, btree-line] ([yshift=0.1cm]sep32.east) -- ([yshift=0.1cm]sep44.west);
            \draw[<-, btree-line] ([yshift=-0.1cm]sep33.east) -- ([yshift=-0.1cm]sep42.west);
            \draw[<-, btree-line] ([yshift=-0.1cm]sep32.east) -- ([yshift=-0.1cm]sep44.west);
            \coordinate[right=0.5cm of sep34.east] (link-sep34);
            \draw[->, btree-line] ([yshift=0.1cm]sep34.east) -- ([yshift=0.1cm]link-sep34.west);
            \coordinate[left=0.5cm of sep43.west] (link-sep43);
            \draw[->, btree-line] ([yshift=0.1cm]sep43.west) -- ([yshift=0.1cm]link-sep43.east);
        \end{tikzpicture}
    \end{overprint}
    \end{center}

    \linespread{0.5}
    \vspace{0.5cm}
    \color{black}\fontsize{6pt}{0}\selectfont
        P. Lehman and S. Yao, Efficient Locking for Concurrent Operations on B-Trees, ACM Transactions on Database Systems, Vol 6, No. 4, December 1981, pp 650-670
    \linespread{1.5}

\fontsize{17pt}{18}\selectfont
\begin{frame}[fragile]{}
    \frametitle{}

    \begin{center}
    \begin{overprint}[12cm]
        \onslide<1>
        \begin{tikzpicture}[]
            \btreenode{1}{}{}{btree-branch}{}
            \btreenode{3}{below=1cm of node1.south west, xshift=-1cm}
                {}{btree-leaf}{}
            \btreenode{4}{below=1cm of node1.south east, xshift=1cm}
                {}{btree-hide}{}
